Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-31 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished section merge close buildings by introducing bridges

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}
\newcommand{\sect}{Sec.~}
\newcommand{\tab}{Tab.~}

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings should be larger than a threshold
\parencite{Regnauld2001,Li2004}.
Following \textcite{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$ for target map. 
The separation threshold at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

If two buildings become too close to each other during growing, 
we merge them by introducing a bridge connecting the nearest points 
(see \fig\ref{fig:GrowAndBridge}).
No matter a bridge appear earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
the same widths.
This setting is achieved by following.
We detect nearest points for each pair of buildings at time $t=0$ so that 
we know where we should add bridges. 
We grow the bridges together with the buildings,
but we do not show the bridges until the two buildings are close enough. 
\todo[inline]{actually larger than $d_{\epsilon, t}$.}

\begin{figure}[tb]
	\centering
	\includegraphics{GrowAndBridge}
	\caption{Merge buildings by introducing bridges when the buildings become 
	too close.
		Although the bridges appear at different time, 
		their widths are the same (see the figure with $t=1$).}
	\label{fig:GrowAndBridge}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=true]{RemovePitAndSpike}
	\caption{Remove a pit by dilating and then remove a spike by eroding.
		(a) a polygon with a pit and a spike;
		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
		(d) dilate the polygon in (c) with distance $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemovePitAndSpike}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=\blndraft]{ErosionBreak}
	\caption{Dilate the gray polygon, then erode the dilated polygon.
		(a) Dilate and erode with distance $d_1$.
		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
		In (a) the result of dilation and erosion is the same as the original 
		polygon, while in (b) the result consists of two parts.
	}
	\label{fig:ErosionBreak}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=\blndraft]{ImaiIri_Shortcut}
	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
	\label{fig:ImaiIri_Shortcut}
\end{figure}

@@

We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. We found that the Imai--Iri 
algorithm fit our needs better.

\subsection{Unite buildings of the immediate previous step}
\label{sec:Unite}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{Shrink_Erosion}
	\caption{A building shrinks during growing because of dilation and erosion, 
	where $t_1=0.6$, $t_2=0.7$, and $t_3=1$.
		The small gray polygons represent the original building.
		(a) Grow and Dilate the building with distances $\dtrm[1]{G}$ and 
		$\dtrm[1]{D}$, respectively;
		(b) Erode the polygon in (a) with distance $\dtrm[1]{D} + \dtrm[1]{E}$;
		(c) Dilate the polygon in (b) with distance $\dtrm[1]{E}$.
		(d) The large gray polygon is the target shape on goal map.
		The process for (e), (f), and (g) is the same as the process of (a), 
		(b), and (c).
		The darker gray piece in (g) shows 
		the part which is included in the grown polygon of (c), 
		but not in the grown polygon of (g).
	}
	\label{fig:Shrink_Erosion}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{Shrink_Simplification}
	\caption{A building shrinks during growing because of line simplification, 
		where $t_1=0.7$, $t_2=0.8$, and $t_3=1$.
		The small gray polygons represent the original building.
		The process for (a), (b), and (c), and 
		the process for (e), (f), and (g) are the same as 
		the processes in \fig\ref{fig:Shrink_Erosion}.
		(d) The large gray polygon is the target shape on goal map.
		(h) Simplify the polygon in (g) using the Imai--Iri algorithm.
		Note that $d_{l,t_1}<d_{l,t_2}$ see \eq\ref{eq:d_lt}),
		which is why the Imai--Iri algorithm does not 
		remove any point of the polygon in (c),
		but removes two points of the polygon in (g).
		The darker gray pieces in (h) show 
		the parts which are included in the polygon of (c), 
		but not in the polygon of (h).
	}
	\label{fig:Shrink_Simplification}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{Shrink_Uniting}
	\caption{Unite a polygon with the polygon at the immediately previous step.
		(a) Unite the polygon of \fig\ref{fig:Shrink_Erosion}~(c) and the 
		polygon of \fig\ref{fig:Shrink_Erosion}~(g);
		(b) Unite the polygon of \fig\ref{fig:Shrink_Simplification}~(c) and 
		the polygon of \fig\ref{fig:Shrink_Simplification}~(h);
	}
	\label{fig:Shrink_Uniting}
\end{figure}

@@

\subsection{Enlarging and merging buildings for goal map}
For each pair of buildings in the same group, 
we find the smallest distance between them.
We connect the buildings by adding an edge from the nearest points.
We find a minimum spanning tree of the buildings using Prim's algorithm 
\parencite{Prim1957}.
We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.

>>>>

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}
\newcommand{\sect}{Sec.~}
\newcommand{\tab}{Tab.~}
\newcommand{\figs}{Figs.~}
\newcommand{\eqs}{Eqs.~}
\newcommand{\sects}{Secs.~}
\newcommand{\tabs}{Tabs.~}

@@

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{RemovePitAndSpike}
	\caption{Remove a pit by dilating and then remove a spike by eroding.
		(a) a polygon with a pit and a spike;
		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
		(d) dilate the polygon in (c) with distance $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemovePitAndSpike}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{ErosionBreak}
	\caption{Dilate the gray polygon, then erode the dilated polygon.
		(a) Dilate and erode with distance $d_1$.
		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
		In (a) the result of dilation and erosion is the same as the original 
		polygon, while in (b) the result consists of two parts.
	}
	\label{fig:ErosionBreak}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{ImaiIri_Shortcut}
	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
	\label{fig:ImaiIri_Shortcut}
\end{figure}

@@

We tried simplifying using 
the Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. 
We found that the Imai--Iri 
algorithm fit our needs better.

\subsection{Unite buildings of the immediately previous step}
\label{sec:Unite}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{Shrink_Erosion}
	\caption{A building shrinks during growing because of dilation and erosion, 
	where $t_1=0.6$, $t_2=0.7$, and $t_3=1$.
		The small gray polygons represent the original building.
		(a) Grow and Dilate the building with distances $\dtrm[1]{G}$ and 
		$\dtrm[1]{D}$, respectively;
		(b) Erode the polygon in (a) with distance $\dtrm[1]{D} + \dtrm[1]{E}$;
		(c) Dilate the polygon in (b) with distance $\dtrm[1]{E}$.
		(d) The large gray polygon is the target shape on goal map.
		The process for (e), (f), and (g) is the same as the process of (a), 
		(b), and (c).
		The darker gray piece in (g) shows 
		the part which is included in the grown polygon of (c), 
		but not in the grown polygon of (g).
	}
	\label{fig:Shrink_Erosion}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[]{Shrink_Simplification}
	\caption{A building shrinks during growing because of line simplification, 
		where $t_1=0.7$, $t_2=0.8$, and $t_3=1$.
		The small gray polygons represent the original building.
		The process for (a), (b), and (c), and 
		the process for (e), (f), and (g) are the same as 
		the processes in \fig\ref{fig:Shrink_Erosion}.
		(d) The large gray polygon is the target shape on goal map.
		(h) Simplify the polygon in (g) using the Imai--Iri algorithm.
		Note that $d_{l,t_1}<d_{l,t_2}$ see \eq\ref{eq:d_lt}),
		which is why the Imai--Iri algorithm does not 
		remove any point of the polygon in (c),
		but removes two points of the polygon in (g).
		The darker gray pieces in (h) show 
		the parts which are included in the polygon of (c), 
		but not in the polygon of (h).
	}
	\label{fig:Shrink_Simplification}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[]{Shrink_Uniting}
	\caption{Unite a polygon with the polygon at the immediately previous step.
		(a) Unite the polygon of \fig\ref{fig:Shrink_Erosion}~(c) and the 
		polygon of \fig\ref{fig:Shrink_Erosion}~(g);
		(b) Unite the polygon of \fig\ref{fig:Shrink_Simplification}~(c) and 
		the polygon of \fig\ref{fig:Shrink_Simplification}~(h);
	}
	\label{fig:Shrink_Uniting}
\end{figure}

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings on a map should be larger than a threshold
\parencite{Regnauld2001,Li2004}.
Following \textcite{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
	\label{eq:d_epsilont}
	d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

If a group of buildings become too close during growing,
we merge them by introducing bridges (see \fig\ref{fig:GrowAndBridge}).
We will talk about where to add bridges in \sect\ref{sec:Goal}.
No matter a bridge appear earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
the same widths.
This setting is achieved by following.
We detect nearest points for each pair of buildings at time $t=0$ so that 
we know where we should add bridges.
At time $t$, we group buildings that are too close to each other,
then we merge them by adding the precomputed bridges.
For this merged building, we grow, simplify, and unite as described in 
\sects\ref{sec:Grow}, \ref{sec:Simplify}, and~\ref{sec:Unite}.
We may unite the processed merged building with several separate parts 
because the group of buildings may be in several smaller groups
in the immediately previous step.

\todo[inline]{actually larger than $d_{\epsilon, t}$.}

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Merge buildings by introducing bridges when the buildings become 
		too close.
		Although the bridges appear at different time, 
		their widths are the same (see the figure with $t=1$).}
	\label{fig:GrowAndBridge}
\end{figure}

For each pair of buildings in the same group, 
we find the smallest distance between them.
We connect the buildings by adding an edge from the nearest points.
We find a minimum spanning tree of the buildings using Prim's algorithm 
\parencite{Prim1957}.
We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.

@@

\subsection{Generate buildings on goal map}
\label{sec:Goal}
We group
